News Across Languages - Cross-Lingual Document Similarity and Event Tracking

### 2015-03-24 rupnik2015.tex
All but Scale fixed

\documentclass[twoside,11pt]{article}
\usepackage{jair, theapa, rawfonts}
\usepackage{graphicx}

@@

\section{Pipeline}

We base our techniques of cross-lingual event linking on an online system for detection of world events, called Event Registry\cite{}. Event Registry is a repository of events, where events are automatically identified by analyzing news articles.  Event Registry works by collecting and analyzing news articles that are published by news outlets in different languages all over the world. Collected articles are first semantically annotated by identifying in them mentions of relevant concepts -- either entities or important keywords. The disambiguated and entity linking of the concepts is done using Wikipedia as the main knowledge base. An online clustering algorithm is then applied on the articles in order to identify groups of articles that are discussing the same event. For each new article, the clustering algorithm determines if the article should be assigned to some existing cluster or into a new cluster. The underlying assumption is that articles that are describing the same event are similar enough and will therefore be put into the same cluster.

The processing is done independently for each language and the output is a clustering of articles in each language, with each cluster ideally representing an event, which are defined by topically, geographically and temporally. The goal of this paper is present approaches to  connecting the clusters/events across languages.

Our approach is based on first defining a similarity function between articles in different languages (Section~\ref{}) and then we present several efficient approaches to linking the clusters based on features (Section~\ref{}). First, however we describe the pre-processing on the input articles which we then take as input.

The system is designed to handle streams and so we describe how a document which enters the stream is processed.   A new document is first tokenized, stop words are removed and words are stemmed. 
 What remains is represented in a vector-space model and normalized using $TF-IDF$ (see Section~\ref{} for the definition). Since each article is tagged with its language, cosine similiarity  is used to find the modst similar existing cluster, by comparing it to the centroid vector of each cluster. A selected threshold is used to determine if the article is not similar to any existing clusters (0.4 was used in our experiments).  The article is then assigned to the corresponding cluster, otherwise a new cluster is created, initially containing only the single article.

The clusters, we consider must have a sufficient number of articles (which is a language dependent paramater). This is to ensure that we consider events. Once an event is identified(i.e. a cluster of sufficient size), a new unique ID is assigned to it and the main information about the event is then automatically extracted by analyzing the articles assigned to it. The extracted information includes properties such as the date of the event, the location, who is involved in it, what the event is about, etc.

 Further details about the system can be found in \cite{}, while our full pipeline is shown in Figure~\ref{}.

\begin{comment}
In short, the article clustering works as follows (details are available in \cite{}). First we create a new document by joining the title and the body of the article. We then tokenize the document, remove the stop words and stem the words. The remaining words are represented as a vector in the vector-space model. Each value in the vector is additionally normalized using TF-IDF. After normalization, we use the vector to find the most similar existing cluster. To be able to compare the vector with a cluster we first need a vector representation for each of the clusters. This is done by computing a centroid vector of the cluster by simply averaging the vectors of the articles in the cluster. By computing the cosine similarity of the article vector with each of the centroid vectors we then find the cluster with the highest similarity. If the highest similarity is above the selected threshold (we used 0.4 in our experiments),

In order to treat the cluster as describing an event in Event Registry,

The clustering of articles is done for each language separately -- English articles are, for example, clustered separately from Spanish articles. When events are identified, they will therefore be identified from clusters in each language separately. As a result, the same event will be represented in Event Registry with two or more event IDs, and each event will only contain coverage in a single language. To avoid this problem we want to exploit the available information about the similarity of the articles in a cluster with articles in other languages. Using this information we hope to be able to connect clusters in different languages and represent them using a single event ID.
\end{comment}
%Event registry $\Rightarrow$ Monolingual events $\Rightarrow$ features (semantic + CCA) $\Rightarrow$ linked events (crosslingual)

@@

An aligned basis is obtained by first splitting $U$ vertically according to the number of dimensions of each language: $U = [U_1^T \cdots U_m^T]^T$. Then, the same as with $k$-means clustering, we compute the pseudoinverses$P_i = (U_i^T U_i)^{-1} U_i^T$. The matrices $P_i$ are used to change the basis from the standard basis in $\RR^{n_i}$ to the basis of columns of $U_i$.

@@

Interpreting the columns of $X_i$ as observation vectors sampled from an underlying distribution $\mathcal{X}_i \in \RR^{n_i}$, the idea is to find two weight vectors $w_i \in \RR^{n_i}$ and $w_j \in \RR^{n_j}$ so that the random variables $w_i^T \cdot \mathcal{X}_i$ and $w_j^T \cdot \mathcal{X}_j$ are maximally correlated ($w_i$ and $w_j$ are used to map the random vectors to random variables, by computing weighted sums of vector components). Let $\rho(x,y)$ denote the sample based correlation coefficient between two vectors of observations $x$ and $y$. By using the sample matrix notation $X_i$ and $X_j$ (assuming no data is missing for clearer presentation) this problem can be formulated as the following optimization problem:

\begin{equation*}
\begin{aligned}
& \underset{w_i \in \RR^{n_i}, w_j \in \RR^{n_j}}{\text{maximize}}
& & \rho(w_i^T X_i , w_j^T X_j) = \frac{w_i^T C_{i,j} w_j}{\sqrt{w_i^T C_{i,i} w_i} \sqrt{w_j^T C_{j,j} w_j}},
\end{aligned}
\end{equation*}

where $C_{i,i}$ and $C_{j,j}$ are empirical estimates of variances of $\mathcal{X}_i$ and $\mathcal{X}_j$ respectively and $C_{i,j}$ is an estimate for the covariance matrix. Assuming that the observation vectors are centered (only for the purposes of presentation), the matrices are computed in the following way: $C_{i,j} = \frac{1}{n-1}X_i X_j^T$, and similarly for $C_{i,i}$ and $C_{j,j}$.
The optimization problem can be reduced to an eigenvalue problem and includes inverting the variance matrices $C_{i,i}$ and $C_{j,j}$. If the matrices are not invertible, one can use a regularization technique by replacing $C_{i,i}$ with $(1- \kappa)C_{i,i} + \kappa I$, where $\kappa \in [0,1]$ is the regularization coefficient and $I$ is the identity matrix (the same can be applied to $C_{j,j}$.
A single canonical variable is usually inadequate in representing the original random vector and typically one looks for $k$ projection pairs $(w_i^1, w_j^1),\ldots,(w_i^k, w_j^k)$, so that $w_i^{uT} \mathcal{X}_i$ and $w_j^{uT} \mathcal{X}_j$ are highly correlated and $w_i^{uT} \mathcal{X}_i$ is uncorrelated with $w_i^{vT} \mathcal{X}_i$  for $u \neq v$ and analogously for $w_j^u$ vectors.

@@

@@

The problem in the second phase of the pipeline is to identify the clusters describing the same events. Each article $a_i$ is written in a language $l$, where $\ell \in L = \{\ell_1,\ell_2,...,\ell_k\}$. For each language $\ell$, we generate and maintain a set of language-specific clusters $C_l$. That is, all articles are in language $l$. For any cluster $c_i \in C_{\ell_a}$, we would like to identify clusters $c_j \in C_{\ell_b}$ (where $\ell_a \neq \ell_b$) that describe the same event as $c_i$. We define \emph{equivalent clusters} as  pairs $(c_i,c_j)$ such that both clusters in the pair describe the same event in languages $C_{\ell_a}$ and $C_{\ell_b}$ respectively. Furthermore, we iterate over all the languages we consider. That is, given a cluster in language $\ell_i$, we look for matching clusters in language $\ell_j$ for $i\neq j$  in a pairwise fashion.

Furthermore, the matching of clusters is a \emph{generalized matching}. We cannot assume that there is only one cluster per language per event, nor can we assume complete coverage - that there exists at least one cluster per event in every language. This implies that we cannot make any assumptions on the matching, e.g. one-to-one, complete, etc. This excludes the use of standard weighted bipartite matching type of algortihms for this problem.

@@

In Section~\ref{sec:models} we have described three main algorithms for identifying similar articles in different languages. These algorithms were $k$-means, LSI and CCA. To test which of these algorithms performs best we performed the following test. Using each algorithm, we analyzed all articles in Event Registry to find the most similar articles in other languages. The values of the cross-lingual article linking features (\texttt{linkCount} and \texttt{avgSimScore}) were then recomputed for all annotated learning examples. A dataset with only these two features and the label was constructed and used to test how accurate prediction models can be induced using the data. The results of the experiment are shown in Table~\ref{table:linkingEvalAlgos}. The table shows for each of the algorithms the obtained classification accuracy, precision and recall. We can see that the most informative features for cluster linking are obtained using the CCA algorithm, while $k$-means performs the worse. Firstly we verified the AMPR performance of approaches by holding out 15000 aligned test documents and using 300000 aligned documents
 as the training set. Picture \cite{pc:AMPR} shows AMPR score as the function of the number of feature vectors. It is clear that CCA outperforms LSI approach and K-means lags far behind.
Then we verified how number of features influences the accuracy of cluster linking. As we can see from Table~\ref{table:linkingEvalAlgosMulti} choosing number of features vectors larger than 500 barely effects linking performance. That is probably due to overfitting.

@@

%AMPR as function of the number of feature vectors
%500 is good, 800 better, 1000 overfitting, noise!
\begin{figure}
\label{pic:AMPR}
\includegraphics{slika.png}
\end{figure}
%Why the hub approach?
%Optimize for language pairs in the system that have the largest number of articles in the system!
%Is star CCA really the best???
%Maybe omit this table?
\begin{table}[h]
\caption{Accuracy of cluster linking with 500 - 800 - 1000 features obtained from different cross-lingual similarity algorithms}
\label{table:linkingEvalAlgosMulti}
\begin{center}
\begin{tabular}{|c|c|c|c|}
  \hline
  \cline{1-4}
  Models & CA & Precision & Recall \\ \cline{1-4}
  CCA & 78.8 - 79.6 - 80.3 \% & 76.9 - 77.9 - 80.2 \%  & 82.1 - 82.3 - 80.4 \%  \\ \cline{1-4}
  LSI & 78.9 - 78.7 - 80.2\% & 76.7 - 76.6 - 78.5 \%  & 82.8 - 82.3 - 82.8 \%  \\ \cline{1-4}
  \hline
\end{tabular}
\end{center}
\end{table}

In the second experiment we wanted to evaluate how relevant individual groups of features are to correctly determine cluster equivalence. For this purpose we tested the accuracies obtained using individual groups of features, as well as using different combination of groups. Since we found the CCA to perform best of the three algorithms, we recomputed it and used it to compute the values of the cross-lingual article linking features. Results of the evaluation are shown in Table~\ref{table:linkingEval}. We can see that using a single group of features, the highest prediction accuracy can be achieved using the concept related features. The classification accuracy in this case is 88.8\%. By additionally including also the cross-lingual article linking features, the classification accuracy rises slightly to 89.2\%. Using all three groups of features, the achieved accuracy is 89.6\%.
Based on the results we can make the following conclusions. The cross-lingual similarity algorithms provide valuable information that can be used to identify clusters that describe the same event in different languages. The computed features are however significantly less informative compared to the features computed on the annotated concepts. Nevertheless, the cross-lingual article similarity features are very important for two reasons. The first reason is that they allow us to identify for a given cluster a limited set of candidate clusters that are potentially equivalent. This is a very important feature since it reduces the search space for several orders of magnitude. The second reason for the importance of these features is that concept annotations are not available for all articles. Annotation of news articles is computationally intensive and can only be done for a subset of collected articles.

\begin{table}[h]
\caption{Accuracy of cluster linking with features obtained from different cross-lingual similarity algorithms}
\label{table:linkingEvalAlgos}
\begin{center}
\begin{tabular}{|c|c|c|c|}
  \hline
  \cline{1-4}
  Models & CA & Precision & Recall \\ \cline{1-4}
  CCA & 77.6\% & 78.3 \%  & 81.1\%  \\ \cline{1-4}
  $k$-means & 73.9\% & 69.5\%  & 84.6\%  \\ \cline{1-4}
  LSI & 76.1\% & 75.5\%  & 76.9\%  \\ \cline{1-4}
  \hline
\end{tabular}
\end{center}
\end{table}

@@

\subsection{Scaling}
\emph{Andrej asks who is the rest? I think that this section should be short.}
100 languages!
%Memory 100 GB per day
%Newsfeed volume 430k articles per day, 210k english, 36k Spanish, 27k German, 17k French, ....
%Number of similarities, 430k similarities every 200ms, currently could handle 1M articles,
%(n \over 2) 500X500 proxy matrices, 300000x500 Projector matrices, 430000x500 data
%Premultiply with proxy matrices, compare blockwise!

>>>>

\documentclass[twoside,11pt]{article}
\usepackage{jair, theapa, rawfonts}
\usepackage{pgfplots} 
%\usepackage{graphicx}

@@

\section{System Overview}

Event registry $\Rightarrow$ Monolingual events $\Rightarrow$ features (semantic + CCA) $\Rightarrow$ linked events (crosslingual)

@@

An aligned basis is obtained by first splitting $U$ vertically according to the number of dimensions of each language: $U = [U_1^T \cdots U_m^T]^T$. Then, the same as with $k$-means clustering, we compute the pseudoinverses $P_i = (U_i^T U_i)^{-1} U_i^T$. The matrices $P_i$ are used to change the basis from the standard basis in $\RR^{n_i}$ to the basis of columns of $U_i$.

@@

Interpreting the columns of $X_i$ as observation vectors sampled from an underlying distribution $\mathcal{X}_i \in \RR^{n_i}$, the idea is to find two weight vectors $w_i \in \RR^{n_i}$ and $w_j \in \RR^{n_j}$ so that the random variables $w_i^T \cdot \mathcal{X}_i$ and $w_j^T \cdot \mathcal{X}_j$ are maximally correlated ($w_i$ and $w_j$ are used to map the random vectors to random variables, by computing weighted sums of vector components). Let $\rho(x,y)$ denote the sample based correlation coefficient between two vectors of observations $x$ and $y$. By using the sample matrix notation $X_i$ and $X_j$ (assuming no data is missing for clearer presentation) this problem can be formulated as the following optimization problem:
\begin{equation*}
\begin{aligned}
& \underset{w_i \in \RR^{n_i}, w_j \in \RR^{n_j}}{\text{maximize}}
& & \rho(w_i^T X_i , w_j^T X_j) = \frac{w_i^T C_{i,j} w_j}{\sqrt{w_i^T C_{i,i} w_i} \sqrt{w_j^T C_{j,j} w_j}},
\end{aligned}
\end{equation*}
where $C_{i,i}$ and $C_{j,j}$ are empirical estimates of variances of $\mathcal{X}_i$ and $\mathcal{X}_j$ respectively and $C_{i,j}$ is an estimate for the covariance matrix. Assuming that the observation vectors are centered (only for the purposes of presentation), the matrices are computed in the following way: $C_{i,j} = \frac{1}{n-1}X_i X_j^T$, and similarly for $C_{i,i}$ and $C_{j,j}$.
The optimization problem can be reduced to an eigenvalue problem and includes inverting the variance matrices $C_{i,i}$ and $C_{j,j}$. If the matrices are not invertible, one can use a regularization technique by replacing $C_{i,i}$ with $(1- \kappa)C_{i,i} + \kappa I$, where $\kappa \in [0,1]$ is the regularization coefficient and $I$ is the identity matrix (the same can be applied to $C_{j,j}$.
A single canonical variable is usually inadequate in representing the original random vector and typically one looks for $k$ projection pairs $(w_i^1, w_j^1),\ldots,(w_i^k, w_j^k)$, so that $(w_i^{u})^T \mathcal{X}_i$ and $(w_j^{u})^T \mathcal{X}_j$ are highly correlated and $(w_i^{u})^T \mathcal{X}_i$ is uncorrelated with $(w_i^{v})^T \mathcal{X}_i$  for $u \neq v$ and analogously for $w_j^u$ vectors.

@@

\begin{comment}
One of the use cases where article linking information can be applied is also in an online system for detection of world events, called Event Registry\cite{}. Event Registry is a repository of events, where events are automatically identified by analyzing news articles. The term event is vague and ambiguous, but for the practical purposes we define it as ``any significant happening that is being reported about in the media''.

Event Registry works by collecting and analyzing news articles that are published by news outlets in different languages all over the world. Collected articles are first semantically annotated by identifying in them mentions of relevant concepts -- either entities or important keywords. The disambiguated and entity linking of the concepts is done using Wikipedia as the main knowledge base. The key step in Event Registry is then to apply an online clustering algorithm on the articles in order to identify groups of articles that are discussing the same event. For each new article, the clustering algorithm determines if the article should be assigned to some existing cluster or into a new cluster. The underlying assumption is that articles that are describing the same event are similar enough and will therefore be put into the same cluster.

In short, the article clustering works as follows (details are available in \cite{}). First we create a new document by joining the title and the body of the article. We then tokenize the document, remove the stop words and stem the words. The remaining words are represented as a vector in the vector-space model. Each value in the vector is additionally normalized using TF-IDF. After normalization, we use the vector to find the most similar existing cluster. To be able to compare the vector with a cluster we first need a vector representation for each of the clusters. This is done by computing a centroid vector of the cluster by simply averaging the vectors of the articles in the cluster. By computing the cosine similarity of the article vector with each of the centroid vectors we then find the cluster with the highest similarity. If the highest similarity is above the selected threshold (we used 0.4 in our experiments), the article is assigned to the corresponding cluster, otherwise a new cluster is created, initially containing only the single article.

In order to treat the cluster as describing an event in Event Registry, the cluster has to grow above a certain number of articles (the number depends on the language). This condition ensures that only content that receives a sufficient coverage in the media is treated as an event. Once a new event is identified, a new unique ID is assigned to it and the main information about the event is then automatically extracted by analyzing the articles assigned to it. The extracted information includes properties such as the date of the event, the location, who is involved in it, what the event is about, etc.

The clustering of articles is done for each language separately -- English articles are, for example, clustered separately from Spanish articles. When events are identified, they will therefore be identified from clusters in each language separately. As a result, the same event will be represented in Event Registry with two or more event IDs, and each event will only contain coverage in a single language. To avoid this problem we want to exploit the available information about the similarity of the articles in a cluster with articles in other languages. Using this information we hope to be able to connect clusters in different languages and represent them using a single event ID.
\end{comment}

@@

The problem in the second phase of the pipeline is to identify the clusters (given?) describing the same events. Each article $a_i$ is written in a language $l$, where $l \in L = \{l_1,l_2,...,l_k\}$. For each language $l$, we generate and maintain a set of language-specific clusters $C_l$. That is, all articles are in language $l$. For any cluster $c_i \in C_{l_a}$, we would like to identify clusters $c_j \in C_{l_b}$ (where $l_a \neq l_b$) that describe the same event as $c_i$. We define \emph{equivalent clusters} as  pairs $(c_i,c_j)$ such that both clusters in the pair describe the same event in languages $C_{l_a}$ and $C_{l_b}$ respectively.

@@

In Section~\ref{sec:models} we have described three main algorithms for identifying similar articles in different languages. These algorithms were $k$-means, LSI and CCA. To test which of these algorithms performs best we performed the following test. Using each algorithm, we analyzed all articles in Event Registry to find the most similar articles in other languages. The values of the cross-lingual article linking features (\texttt{linkCount} and \texttt{avgSimScore}) were then recomputed for all annotated learning examples. A dataset with only these two features and the label was constructed and used to test how accurate prediction models can be induced using the data. The results of the experiment are shown in Table~\ref{table:linkingEvalAlgos}. The table shows for each of the algorithms the obtained classification accuracy, precision and recall. We can see that the most informative features for cluster linking are obtained using the CCA algorithm, while $k$-means performs the worse. Firstly we verified the AMRR (average of mean reciprocal ranks over all language pairs) performance of approaches by holding out $15000$ aligned test documents and using $300000$ aligned documents
 as the training set. Picture \ref{pc:AMRR} shows AMRR score as the function of the number of feature vectors. It is clear that CCA outperforms LSI approach and K-means lags far behind.
Furthermore we inspected how number of features influences the accuracy of cluster linking. As we can see from Table~\ref{table:linkingEvalAlgos} choosing number of features vectors larger than $500$ barely effects linking performance. That is probably due to overfitting. Moreover we tested the performance of detecting large/small cluster linking. As expected we obtained that it is harder to link small clusters and we need better retrieval. Hub CCA outperform other methods in this sense also, probably as it has the best retrieval performance, see Figure~\ref{pic:AMRR}.

@@

%AMPR as function of the number of feature vectors
%500 is good, 800 better, 1000 overfitting, noise!
\begin{figure}
\caption{Average of mean reciprocal ranks}
\label{pic:AMRR}
%\includegraphics{slika.png}
\input{retrieval}
\end{figure}
%Why the hub approach?
%Optimize for language pairs in the system that have the largest number of articles in the system!
%Is star CCA really the best???
%Maybe omit this table?
\begin{table}[h]
\caption{Accuracy of cluster linking with 500 - 800 - 1000 features obtained from different cross-lingual similarity algorithms}
\label{table:linkingEvalAlgos}
\begin{center}
\begin{tabular}{|c|c|c|c|}
  \hline
  \cline{1-4}
  Models & CA & Precision & Recall \\ \cline{1-4}
  CCA      & 78.2 - 79.6 - 80.3 \% & 76.3 - 78.0 - 80.5 \%  & 81.6 - 82.1 - 79.9 \%  \\ \cline{1-4}
  LSI      & 78.9 - 78.7 - 80.6 \%  & 76.8 - 77.0 - 78.7 \%  & 83.3 - 80.6 - 83.6 \%  \\ \cline{1-4}
 $k$-means & 73.9\phantom{ - 78.7 - 80.6 }\% & 69.5\phantom{ - 78.7 - 80.6 }\%  & 84.6\phantom{ - 78.7 - 80.6 }\%  \\ \cline{1-4}
\end{tabular}
\end{center}
\end{table}

\begin{table}[h]
\caption{Accuracy of large/small cluster linking with $500$ features obtained from different cross-lingual similarity algorithms}
\label{table:linkingEvalAlgosLargeSmall}
\begin{center}
\begin{tabular}{|c|c|c|c|}
  \hline
  \cline{1-4}
  Models & CA & Precision & Recall \\ \cline{1-4}
  CCA      & 81.2 - 77.8 \% & 80.5 - 74.5 \%  & 91.3 - 57.5 \%  \\ \cline{1-4}
  LSI      & 82.8 - 76.4 \% & 81.3 - 70.9 \%  & 93.1 - 57.5 \%  \\ \cline{1-4}
 $k$-means & 75.5 - 71.2 \% & 72.8 - 70.8 \%  & 95.3 - 36.2 \%  \\ \cline{1-4}
\end{tabular}
\end{center}
\end{table}

In the second experiment we wanted to evaluate how relevant individual groups of features are to correctly determine cluster equivalence. For this purpose we tested the accuracies obtained using individual groups of features, as well as using different combination of groups. Since we found the CCA to perform best of the three algorithms, we recomputed $500$ feature vectors with better accuracy and used it to compute the values of the cross-lingual article linking features. Results of the evaluation are shown in Table~\ref{table:linkingEval}. We can see that using a single group of features, the highest prediction accuracy can be achieved using the concept related features. The classification accuracy in this case is 88.8\%. By additionally including also the cross-lingual article linking features, the classification accuracy rises slightly to 89.2\%. Using all three groups of features, the achieved accuracy is 89.6\%.
Based on the results we can make the following conclusions. The cross-lingual similarity algorithms provide valuable information that can be used to identify clusters that describe the same event in different languages. The computed features are however significantly less informative compared to the features computed on the annotated concepts. Nevertheless, the cross-lingual article similarity features are very important for two reasons. The first reason is that they allow us to identify for a given cluster a limited set of candidate clusters that are potentially equivalent. This is a very important feature since it reduces the search space for several orders of magnitude. The second reason for the importance of these features is that concept annotations are not available for all articles. Annotation of news articles is computationally intensive and can only be done for a subset of collected articles.

%\begin{table}[h]
%\caption{Accuracy of cluster linking with features obtained from different cross-lingual similarity algorithms}
%\label{table:linkingEvalAlgos}
%\begin{center}
%\begin{tabular}{|c|c|c|c|}
%  \hline
%  \cline{1-4}
%  Models & CA & Precision & Recall \\ \cline{1-4}
%  CCA & 77.6\% & 78.3 \%  & 81.1\%  \\ \cline{1-4}
%  $k$-means & 73.9\% & 69.5\%  & 84.6\%  \\ \cline{1-4}
%  LSI & 79.2\% & 78.9\%  & 80.6\%  \\ \cline{1-4}
%  \hline
%\end{tabular}
%\end{center}
%\end{table}

@@

\subsection{Scaling}
\emph{I think that this section should be short.}
100 languages!
%Memory 100 GB per day
%Newsfeed volume 430k articles per day, 210k english, 36k Spanish, 27k German, 17k French, ....
%Number of similarities, 430k similarities every 200ms, currently could handle 1M articles,
%(n \over 2) 500X500 proxy matrices, 300000x500 Projector matrices, 430000x500 data
%Premultiply with proxy matrices, compare blockwise!
